Mutual Coherence Minimization \\via Projection Matrices\\ for CSM EENG 515

### 2018-12-10 paper.tex
new changes

paper, several norms are used. First we define the $l_\infty$ norm:

@@

Note that this is simply the largest entry in the matrix. This should not be confused with other 
norms which take the largest row sum. Next we define the Frobenius norm:

@@

This can be thought of as vectorizing $A$, then computing it's vector $l_2$ norm.  To define the vector 
$l_2$ norm:

@@

||X||_2 = \sqrt{\sum_{i} |x_{i}|^2}, \quad X \in \mathbb{R}^{n}

@@

Eqn~\ref{eq:vecl2} is a commonly used norm and is a member of the $l_p$ norms. Another such member from
this family of norms is the $l_1$ norm. Again in this case we use the vectorized version:

@@

||A||_1 = \sqrt{\sum_{i,j} |a_{ij}|}, \quad A \in \mathbb{R}^{m\times n}

@@

Finally, there is one more norm which is used throughout this paper which is the $l_0$ norm. This 

@@

how sparse a signal is. \\

@@

Because this problem uses the $l_0$ norm, the problem is not immediately tractable. Some transformations

@@

One method for transforming this problem, involves transitioning from the $l_0$ norm to the $l_1$ norm.

@@

@@

@@

\mu_{WB}(M) \geq \sqrt{\frac{n - m}{m(n-1}}

@@

There have been different techniques used to minimize MC recently, some of which include: $\ldots$ \\

@@

\pagebreak %optional

@@

@@

Lin's method for mutual coherence minimization involves estimating the gradient of the dictionary
($\Delta D$) through a projection onto the $l_1$ ball. $\ldots$ \\

@@

And to iterate for new values of D:

@@

    D_{k+1} = \frac{2}{3}

@@

@@

Then it has MC and Welch bound:

@@

@@

>>>>

paper, several norms are used, each of which treats the input as a vector. First we define the matrix $\ell_\infty$ norm:

@@

Note that this is simply the largest entry in the matrix. This should not be confused with other definition of matrix $\ell_\infty$ norm, which take the largest row absolute sum (latter definition we used in the class). Next we define the Frobenius norm:

@@

This can be thought of as vectorizing $A$, then computing its vector $\ell_2$ norm.  To define the vector 
$\ell_2$ norm:

@@

||x||_2 = \sqrt{\sum_{i} |x_{i}|^2}, \quad X \in \mathbb{R}^{n}

@@

Equation~\ref{eq:vecl2} is a commonly used norm and is a member of the $\ell_p$ norms,  where $1\leq p < \infty$. Another such member from
this family of norms is the $\ell_1$ norm. Again in this case we use the vectorized version:

@@

||A||_1 = \sum_{i,j} |a_{ij}|, \quad A \in \mathbb{R}^{m\times n}

@@

Also, there is another definition of the matrix $\ell_1$ norm, we used in the class, which states that the $\ell_1$ norm of the matrix is the largest absolute column sum.\\ 
Finally, there is one more norm which is used throughout this paper which is the $\ell_0$ norm, which is non-convex and does not belong to the  $\ell_p$ norms family, where $1\leq p < \infty$.  This 

@@

how sparse a signal is. 

@@

Because this problem uses the $\ell_0$ norm, the problem is not immediately tractable. Some transformations

@@

One method for transforming this problem, involves transitioning from the $\ell_0$ norm to the $\ell_1$ norm.

@@

\mu(M)=\max\limits_{\substack{1\leq i,j \leq n \\ i\neq j}}\frac{|\langle (M)_i, (M)_j \rangle |}{\|(M)_i\| \|(M)_j\|},

@@

where $ (M)_i$ denotes the $i$-th column of $M$ and $\langle\cdot , \cdot \rangle $ denotes the standard inner product in $\mathbb{R}^n$. 

@@

\mu_{WB}(M) \geq \sqrt{\frac{n - m}{m(n-1)}}

@@

There have been different techniques used to minimize MC recently, some of which include: the algorithm of Elad [Elad's paper], the algorithm of Duarte-Carajalino and Sapiro [DC and S paper], the algorithm of Xu et al [Xu's paper], and the algorithm of Obermeier and Martinez-Lorenzo [Obermeeir's paper]. 
\begin{figure}[!h]
\centering
\includegraphics[width=2.8in]{comparison.png}
\caption{Plots of the averaged mutual coherence of a matrix of size $m \times n$ v.s. number of rows $m$.}
\label{Fig:comp_of_algtms}
\end{figure}

$\ldots$ \\

@@

%\pagebreak %optional

@@

\subsection{Projection onto $l_1$ ball}

@@

The method of Lin et al. for direct mutual coherence minimization involves estimating the gradient of the dictionary
($\Delta D$) through a projection onto the $l_1$ ball. A factor $V$ must be calculated which is
the projection of $(D_k^T D_k - I)/ \rho $ onto the $l_1$ ball.

@@

And to iterate for new columns of D:
This method represents the proximal gradient method for mutual coherence minimization.

@@

    (D_{k+1})_i = \frac{(D_k)_i - \alpha (\Delta D_k)_i}{||(D_k)_i - \alpha (\Delta D_k)_i||_2}

@@

\subsection{Low Dimensional Example}
\begin{figure}[!h]
\centering
\includegraphics[width=2.8in]{lowdimhighmc.eps}
\caption{A linearly dependant spanning set for $\mathbb{R}^2$.}
\label{Fig:lowdimhigh}
\end{figure}
\noindent The following example will help illustrate the application of Mutual Coherence minimization
to an overcomplete dictionary. The dictionary is chosen to be low dimensional so the concept
of mutual coherence minimization can be illustrated clearly.

@@

Shown in Fig. \ref{Fig:lowdimhigh}, $D$ will have its Mutual Coherence minimized through this gradient 
descent problem.
It has initial MC and Welch bound:

@@

This new dictionary is shown in Fig.~\ref{Fig:lowdimlow}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=2.8in]{lowdimlowmc.eps}
\caption{A less linearly dependant spanning set for $\mathbb{R}^2$. The absolute value
of the inner product has been minimized for this number of vectors in $\mathbb{R}^2$.}
\label{Fig:lowdimlow}
\end{figure}
%\pagebreak \\
The algorithm of Lin et al. quickly reduces the mutual coherence of the dictionary in the first iteration while then taking some time to settle to a final solution. This is shown in Fig.~\ref{Fig:mcvk}.
\begin{figure}[!t]
\centering
\includegraphics[width=2.8in]{MCvk.eps}
\caption{The MC falls quiclkly in the first iteration before oscilating wildly on its way towards a
steady solution.}
\label{Fig:mcvk}
\end{figure}
\bigskip \\
